Covid-19 Fields Survey Data Protocol

### 2023-01-25 protocol/Background_and_methods_Jan_24.tex
Working on model and results

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{multicol}
\usepackage{hhline}
\usepackage{hyperref}
\usepackage{placeins}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Covid-19 Fields Survey Data Protocol},
  pdfauthor={Ariel Mundo Ortiz},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/16/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

\hypertarget{tbl-covariates}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2361}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7639}}@{}}
\caption{\label{tbl-covariates}Selected socio-economic factors from the
survey}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Variable
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Values
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Variable
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Values
\end{minipage} \\
\midrule()
\endhead
Age group & 15-24,25-34,35-44,45-54,55-64, 65+ \\
Income bracket (CAD) & \textless15,000, 15,000-24,999, 25,000-39,999,
40,000-59,999, 60,000-89,999, \textgreater90,000 \\
Race/ethnicity & Arab/Middle Eastern, Black, East Asian/Pacific
Islander, Indigenous, Latin American, Mixed, South Asian, White
Caucasian, other \\
& \\
\bottomrule()
\end{longtable}

@@

For each survey participant certain data was automatically captured.
This included the nearest municipality, which resulted in a total of 578
different municipalities within the dataset. Because our interest was to
analyze the differences between Health Regions, we assigned the location
(city) of each entry to its correspondent Health Region following a
multi-step process: First, we used the municipality information from the
website of the Association of Municipalities of Ontario (AMO) to assign
geographical regions to each entry on the dataset. Secondly, we used a
publicly available dataset of long-term care homes by Local Health
Integrated Network (LHIN), which were the geographical divisions for
health in Ontario before the adoption of the Health Regions, to match
each city with its corresponding LHIN. Cities that did not have a LHIN
entry on the dataset were searched in the websites of the LHINs and
manually added to the dataset. Finally, we assigned the corresponding
Health Regio to each city by matching the LHINs to the Health Regions
that now encompass them, following the information provided by Ontario
Health (details of the complete process are in the Appendix).

@@

\hypertarget{statistical-models}{%
\subsection{Statistical models}\label{statistical-models}}

@@

Therefore, we built different logistic regression models that accounted
for different levels of interaction between the available socio-economic
factors obtained from the Fields Covid survey. The different models are
described below.

\hypertarget{model-building-and-selection}{%
\subsubsection{Model building and
selection}\label{model-building-and-selection}}

The first model (\texttt{model1}) examined the interaction of income and
Health Region as it has been shown that there has been an increase in
income inequality within the provinces of Canada over
time\textsuperscript{\protect\hyperlink{ref-marchand2020}{26}}, and the
relatively recent implementation of the Health Regions motivated us to
explore if income disparity may be an important factor to consider
within each of the Health Regions.

The the model was fitted using the function \texttt{svyglm} from the
\texttt{survey} R package in order to incorporate the correction in
sampling probability obtained from raking. The model appears in
Equation~\ref{eq-model1}.

\begin{equation}\protect\hypertarget{eq-model1}{}{
\begin{aligned}
\log \left( \frac{p\textrm{(vac)}}{1-p\textrm{(vac)}} \right) = \beta_0+ \beta_{1}\textrm{(Age group)} +\beta_{2} \textrm{ Race} +\\ \beta_3 \textrm{ Health Region} + \beta_4 \textrm{ Income} + \beta_5\textrm{(Health Region} \times \textrm{Income)}
\end{aligned}
}\label{eq-model1}\end{equation}

Where \(p\textrm{(vac)}\) indicates the probability of having received
the first dose of a Covid-19 vaccine.

The second model (\texttt{model2}) incorporated an interaction effect
between age group and income to examine if a significant interaction
occured between these factors as well. The model appears in
Equation~\ref{eq-model2}.

\begin{equation}\protect\hypertarget{eq-model2}{}{
\begin{aligned}
\log \left( \frac{p\textrm{(vac)}}{1-p\textrm{(vac)}} \right) = \beta_0+ \beta_{1}\textrm{(Age group)} +\beta_{2} \textrm{ Race} + \beta_3 \textrm{ Health Region} + \\\beta_4 \textrm{ Income}+ \beta_5\textrm{(Health Region} \times \textrm{Income)} + \beta_6 \textrm{ (Age group} \times \textrm{Income)}
\end{aligned}
}\label{eq-model2}\end{equation}

A third model (\texttt{model3}) incorporated an interaction effect
between race and income, and appears in Equation~\ref{eq-model3}.

@@

Although it could have been interesting to examine the interaction of
Health Region and Race, or 3-way interactions between socio-economic
factors (e.g., age,income,race), these models had singularity issues.
Next, we compared the AIC of the three models indicated above. The AICs
are very similar and appear in Table~\ref{tbl-AIC}.

\hypertarget{tbl-AIC}{}
\begin{table}
\caption{\label{tbl-AIC}AIC for the three models }\tabularnewline

\centering
\begin{tabular}[t]{rl}
\toprule
AIC & model\\
\midrule
3580.878 & model1\\
3614.465 & model2\\
3633.575 & model3\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{tbl-descriptive-stats}{}
\begin{table}[H]

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\begin{longtable}[c]{|p{2.35in}|p{1.21in}|p{1.27in}}

\caption{\label{tbl-descriptive-stats}Descriptive Statistics of the Fields Covid-19 Survey } \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Variable}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{no,\ N\ =\ 1,000}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{yes,\ N\ =\ 2,709}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{1}}}} \\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}-}\endhead

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Income}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{15000\_24999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{167\ (34\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{326\ (66\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{25000\_39999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{144\ (31\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{316\ (69\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{40000\_59999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{116\ (25\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{348\ (75\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{60000\_89999}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{71\ (17\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{343\ (83\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{over\_90000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{251\ (25\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{752\ (75\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{under\_15000}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{251\ (29\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{624\ (71\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textbf{Age\_group}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.35in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{16\_24}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.21in+0\tabcolsep+0\arrayrulewidth}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{230\ (27\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.27in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{634\ (73\%)}}} \\

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{placeins}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Covid-19 Fields Survey Data Protocol},
  pdfauthor={Ariel Mundo Ortiz},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/24/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\hypertarget{tbl-covariates}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7500}}@{}}
\caption{\label{tbl-covariates}Selected socio-economic factors from the
survey}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Variable
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Values
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Variable
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Values
\end{minipage} \\
\midrule()
\endhead
Age group & 15-24,25-34,35-44,45-54,55-64, 65+ \\
Income bracket (CAD) & \textless15,000, 15,000-24,999, 25,000-39,999,
40,000-59,999, 60,000-89,999, \textgreater90,000 \\
Race/ethnicity & Arab/Middle Eastern, Black, East Asian/Pacific
Islander, Indigenous, Latin American, Mixed, South Asian, White
Caucasian, other \\
& \\
\bottomrule()
\end{longtable}

@@

For each survey participant certain data was automatically captured.
This included the nearest municipality, which resulted in a total of 578
different municipalities within the dataset. Because our interest was to
analyze the differences between Health Regions, we assigned the location
(city) of each entry to its correspondent Health Region following a
multi-step process: First, we used the municipality information from the
website of the Association of Municipalities of Ontario (AMO) to assign
geographical regions to each entry on the dataset. Secondly, we used a
publicly available dataset of long-term care homes by Local Health
Integrated Network (LHIN), which were the geographical divisions for
health in Ontario before the adoption of the Health Regions, to match
each city with its corresponding LHIN. Cities that did not have a LHIN
entry on the dataset were searched in the websites of the LHINs and
manually added to the dataset. Finally, we assigned the corresponding
Health Region to each city by matching the LHINs to the Health Regions
that now encompass them, following the information provided by Ontario
Health (details of the complete process are in the Appendix).

Following an assessment of the number of entries corresponding to each
Health Region in the clean dataset, there were a relatively low number
of observations from the North East and North West regions (2.9\% and
1.4\% of the total clean dataset, respectively). Due to the low number
of entries in each case, we omitted the entries from these regions from
further analyses. Therefore, the total number of unique entries used for
analysis was 3,551.

@@

\hypertarget{statistical-model}{%
\subsection{Statistical model}\label{statistical-model}}

@@

Therefore, we built a logistic regression model that accounted for
interactions between the available socio-economic factors obtained from
the Fields Covid survey. The model appears in Equation~\ref{eq-model3},

@@

Where \(p\textrm{(vac)}\) indicates the probability of having received
the first dose of a Covid-19 vaccine, \(\beta_0\) indicates the
population intercept, \(\beta_1...\beta_7\) indicate the coefficients
for each of the fixed and interaction effects of age group, race, Health
Region, and income. The the model was fitted using the function
\texttt{svyglm} from the \texttt{survey} R package in order to
incorporate the correction in sampling probability obtained from raking.

\begin{table}

@@

\hypertarget{tbl-descriptive-stats}{}
\begin{table}
\caption{\label{tbl-descriptive-stats}Descriptive Statistics of the Fields Covid-19 Survey }\tabularnewline

\centering\begingroup\fontsize{9}{11}\selectfont

\begin{tabular}{lcc}
\toprule
\textbf{Variable} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,593\\
\midrule
\textbf{Income} &  & \\
\hspace{1em}over\_90000 & 238 (25\%) & 722 (75\%)\\
\hspace{1em}15000\_24999 & 160 (34\%) & 315 (66\%)\\
\hspace{1em}25000\_39999 & 140 (32\%) & 302 (68\%)\\
\hspace{1em}40000\_59999 & 113 (25\%) & 334 (75\%)\\
\addlinespace
\hspace{1em}60000\_89999 & 67 (17\%) & 327 (83\%)\\
\hspace{1em}under\_15000 & 240 (29\%) & 593 (71\%)\\
\textbf{Age\_group} &  & \\
\hspace{1em}16\_24 & 223 (27\%) & 614 (73\%)\\
\hspace{1em}25\_34 & 186 (27\%) & 498 (73\%)\\
\addlinespace
\hspace{1em}35\_44 & 129 (25\%) & 385 (75\%)\\
\hspace{1em}45\_54 & 123 (27\%) & 327 (73\%)\\
\hspace{1em}55\_64 & 75 (20\%) & 299 (80\%)\\
\hspace{1em}65\_and\_over & 222 (32\%) & 470 (68\%)\\
\textbf{Health\_Region} &  & \\
\addlinespace
\hspace{1em}Toronto & 371 (28\%) & 953 (72\%)\\
\hspace{1em}Central & 224 (28\%) & 581 (72\%)\\
\hspace{1em}East & 135 (23\%) & 448 (77\%)\\
\hspace{1em}West & 228 (27\%) & 611 (73\%)\\
\textbf{Race} &  & \\
\addlinespace
\hspace{1em}white\_caucasian & 233 (18\%) & 1,080 (82\%)\\
\hspace{1em}arab\_middle\_eastern & 76 (36\%) & 138 (64\%)\\
\hspace{1em}black & 114 (38\%) & 184 (62\%)\\
\hspace{1em}east\_asian\_pacific\_islander & 69 (23\%) & 234 (77\%)\\
\hspace{1em}indigenous & 76 (40\%) & 115 (60\%)\\
\addlinespace
\hspace{1em}latin\_american & 69 (38\%) & 111 (62\%)\\
\hspace{1em}mixed & 105 (34\%) & 205 (66\%)\\
\hspace{1em}other & 128 (35\%) & 239 (65\%)\\
\hspace{1em}south\_asian & 88 (23\%) & 287 (77\%)\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}
\endgroup{}
\end{table}

\hypertarget{vaccination-status-socio-economic-and-geographical-variables}{%
\subsection{Vaccination status, socio-economic and geographical
variables}\label{vaccination-status-socio-economic-and-geographical-variables}}

Table~\ref{tbl-model} shows the results of the logistic regression on
vaccination status using socio-economic, geographical factors (by Health
Region) and their interactions as predictors. The reference groups in
each case were set as follow: 16 to 24 years (age group), White
Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income).
Socio-economic factors with statistically significant odds ratios were
the age group of 65 years and over (OR=0.58), persons who identified as
Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27),
Latin American (OR=0.24), South Asian (OR=0.17) and Other Race/Ethnicity
(a group that included minorities not found elsewhere, OR=0.17), and
those that lived in a household with an income bracket between CAD
25,000 and CAD 39,999.

Regarding the interaction of socio-economic and geographical factors,
statistically significant odds ratios were the Central Health Region and
Income of 15000 to 24999 CAD (OR=0.4), Age Group of 65 years and older
with a household income between 25000 and 39999 CAD (OR=0.001), and with
an income between 40000 and 59999 (OR=3.12)

\hypertarget{tbl-model}{}
\begin{longtable}{lccc}
\caption{\label{tbl-model}Multiple Regression Analysis-Predictors of Vaccination Status }\tabularnewline

\toprule
\textbf{Characteristic} & \textbf{OR} & \textbf{95\% CI} & \textbf{p-value}\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
\textbf{Characteristic} & \textbf{OR} & \textbf{95\% CI} & \textbf{p-value}\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\textbf{Age Group} &  &  & \\
\hspace{1em}16\_24 & — & — & \\
\hspace{1em}25\_34 & 0.58 & 0.26, 1.28 & 0.2\\
\hspace{1em}35\_44 & 0.72 & 0.33, 1.57 & 0.4\\
\hspace{1em}45\_54 & 0.53 & 0.25, 1.13 & 0.10\\
\addlinespace
\hspace{1em}55\_64 & 0.94 & 0.42, 2.09 & 0.9\\
\hspace{1em}65\_and\_over & 0.44 & 0.22, 0.86 & 0.017\\
\textbf{Race} &  &  & \\
\hspace{1em}white\_caucasian & — & — & \\
\hspace{1em}arab\_middle\_eastern & 0.15 & 0.07, 0.35 & <0.001\\
\addlinespace
\hspace{1em}black & 0.17 & 0.09, 0.34 & <0.001\\
\hspace{1em}east\_asian\_pacific\_islander & 0.83 & 0.40, 1.75 & 0.6\\
\hspace{1em}indigenous & 0.27 & 0.11, 0.62 & 0.002\\
\hspace{1em}latin\_american & 0.24 & 0.10, 0.58 & 0.002\\
\hspace{1em}mixed & 0.49 & 0.23, 1.03 & 0.059\\
\addlinespace
\hspace{1em}other & 0.17 & 0.10, 0.31 & <0.001\\
\hspace{1em}south\_asian & 0.40 & 0.20, 0.79 & 0.009\\
\textbf{Health Region} &  &  & \\
\hspace{1em}Toronto & — & — & \\
\hspace{1em}Central & 1.12 & 0.69, 1.82 & 0.6\\
\addlinespace
\hspace{1em}East & 1.07 & 0.59, 1.93 & 0.8\\
\hspace{1em}West & 1.21 & 0.72, 2.04 & 0.5\\
\textbf{Income} &  &  & \\
\hspace{1em}over\_90000 & — & — & \\
\hspace{1em}15000\_24999 & 0.42 & 0.15, 1.19 & 0.10\\
\addlinespace
\hspace{1em}25000\_39999 & 0.23 & 0.08, 0.69 & 0.009\\
\hspace{1em}40000\_59999 & 0.49 & 0.16, 1.43 & 0.2\\
\hspace{1em}60000\_89999 & 0.84 & 0.26, 2.72 & 0.8\\
\hspace{1em}under\_15000 & 0.40 & 0.16, 1.02 & 0.055\\
\textbf{Health Region * Income} &  &  & \\
\addlinespace
\hspace{1em}Central * 15000\_24999 & 0.40 & 0.17, 0.97 & 0.043\\
\hspace{1em}East * 15000\_24999 & 1.43 & 0.54, 3.74 & 0.5\\
\hspace{1em}West * 15000\_24999 & 0.63 & 0.28, 1.43 & 0.3\\
\hspace{1em}Central * 25000\_39999 & 0.99 & 0.42, 2.31 & >0.9\\
\hspace{1em}East * 25000\_39999 & 0.96 & 0.36, 2.57 & >0.9\\
\addlinespace
\hspace{1em}West * 25000\_39999 & 0.97 & 0.41, 2.29 & >0.9\\
\hspace{1em}Central * 40000\_59999 & 1.01 & 0.42, 2.40 & >0.9\\
\hspace{1em}East * 40000\_59999 & 0.86 & 0.33, 2.22 & 0.8\\
\hspace{1em}West * 40000\_59999 & 0.64 & 0.27, 1.50 & 0.3\\
\hspace{1em}Central * 60000\_89999 & 2.92 & 0.91, 9.33 & 0.071\\
\addlinespace
\hspace{1em}East * 60000\_89999 & 1.58 & 0.48, 5.18 & 0.4\\
\hspace{1em}West * 60000\_89999 & 1.48 & 0.54, 4.04 & 0.4\\
\hspace{1em}Central * under\_15000 & 0.80 & 0.39, 1.63 & 0.5\\
\hspace{1em}East * under\_15000 & 1.11 & 0.46, 2.73 & 0.8\\
\hspace{1em}West * under\_15000 & 0.66 & 0.31, 1.39 & 0.3\\
\addlinespace
\textbf{Age Group * Income} &  &  & \\
\hspace{1em}25\_34 * 15000\_24999 & 0.97 & 0.30, 3.09 & >0.9\\
\hspace{1em}35\_44 * 15000\_24999 & 0.68 & 0.21, 2.19 & 0.5\\
\hspace{1em}45\_54 * 15000\_24999 & 1.17 & 0.33, 4.10 & 0.8\\
\hspace{1em}55\_64 * 15000\_24999 & 2.81 & 0.63, 12.5 & 0.2\\
\addlinespace
\hspace{1em}65\_and\_over * 15000\_24999 & 1.54 & 0.50, 4.69 & 0.5\\
\hspace{1em}25\_34 * 25000\_39999 & 2.68 & 0.80, 8.95 & 0.11\\
\hspace{1em}35\_44 * 25000\_39999 & 2.37 & 0.64, 8.78 & 0.2\\
\hspace{1em}45\_54 * 25000\_39999 & 2.12 & 0.63, 7.11 & 0.2\\
\hspace{1em}55\_64 * 25000\_39999 & 1.59 & 0.42, 6.05 & 0.5\\
\addlinespace
\hspace{1em}65\_and\_over * 25000\_39999 & 7.21 & 2.20, 23.6 & 0.001\\
\hspace{1em}25\_34 * 40000\_59999 & 2.18 & 0.66, 7.19 & 0.2\\
\hspace{1em}35\_44 * 40000\_59999 & 1.48 & 0.43, 5.04 & 0.5\\
\hspace{1em}45\_54 * 40000\_59999 & 2.57 & 0.72, 9.13 & 0.15\\
\hspace{1em}55\_64 * 40000\_59999 & 1.09 & 0.28, 4.18 & >0.9\\
\addlinespace
\hspace{1em}65\_and\_over * 40000\_59999 & 3.12 & 1.03, 9.50 & 0.045\\
\hspace{1em}25\_34 * 60000\_89999 & 0.47 & 0.12, 1.89 & 0.3\\
